Interval-based Robust Control of Linear Systems with Generic Costs

### 2020-05-27 main.tex
Update code readme

\paragraph{Outline}
In \Cref{sec:proof}, we provide a proof for every novel result introduced in this paper. \Cref{sec:attachments} describes the attached video files and source code. \Cref{sec:tight-polytope} gives a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}. \Cref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem. Finally, \Cref{sec:experimental-setting} provides additional details on our experiments.

@@

\paragraph{Source code}
The attached \texttt{code} directory contains an implementation of \Cref{alg:full}. We relate the algorithmic steps of this paper to their location in the source code.
\begin{enumerate}
	\item The confidence ellipsoid \eqref{eq:confidence-ellipsoid} is implemented in the \texttt{ellipsoid()} method in \url{code/rl_agents/agents/tree_search/robust_epc.py}
	\item The corresponding polytope \eqref{eq:polytope} is implemented in the \texttt{polytope()} method of \url{code/rl_agents/agents/tree_search/robust_epc.py}
	\item The simple predictor of \eqref{eq:predictor-naive} is implemented in the \texttt{step\_simple\_predictor()} method of \url{code/rl_agents/agents/common/interval.py}
	\item The enhanced predictor of \eqref{eq:interval-predictor} is implemented in the \texttt{step\_interval\_predictor()} method of \url{code/rl_agents/agents/common/interval.py}
	\item The pessimistic reward of \eqref{eq:surrogate-objective} is implemented in the \texttt{pessimistic\_reward()} method of \url{code/obstacle_env/envs/obstacle.py} and the \texttt{check\_collision()} method of \url{code/highway_env/vehicle/uncertainty/prediction.py}
	\item The robust upper-bound of \eqref{eq:robust-b-values} is implemented in the \texttt{RobustNode} class of \url{code/rl_agents/agents/tree_search/robust.py}
\end{enumerate}
The experiments can be reproduced by running:
\lstset{language=bash}
\begin{lstlisting}
cd scripts
python experiments.py configs/<env>/env.json configs/<env>/agents/<agent>.json
\end{lstlisting}

@@

\paragraph{States}
\paragraph{Actions}
\paragraph{Reward}
\paragraph{Dynamics}

>>>>

\paragraph{Outline}
In \Cref{sec:proof}, we provide a proof for every novel result introduced in this paper. \Cref{sec:attachments} describes the attached video files and source code. \Cref{sec:experimental-setting} provides additional details on our experiments. \Cref{sec:tight-polytope} gives a better method of conversion from ellipsoid to polytope than that of \eqref{eq:polytope}. Finally, \Cref{sec:min-max-order} highlights the fact that robustness cannot be recovered by aggregating independent solutions to many optimal control problem.

@@

\paragraph{Source code}
The attached \texttt{code} directory contains an implementation of \Cref{alg:full}. The \texttt{README.md} file relates the algorithmic steps of this paper to their location in the source code, and contains instructions to reproduce our experimental results.

@@

\paragraph{Actions}
\paragraph{Reward}
\paragraph{Dynamics}

$
\begin{bmatrix}
\dot{p_x}\\
\dot{p_y}\\
\dot{v_x}\\
\dot{v_y}\\
\end{bmatrix} = 
\begin{bmatrix}
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1 \\
0 & 0 & -\theta_x & 0 \\
0 & 0 & 0 & -\theta_y
\end{bmatrix}
\begin{bmatrix}
{p_x}\\
{p_y}\\
{v_x}\\
{v_y}\\
\end{bmatrix}
+
\begin{bmatrix}
0\\
0\\
{u_x}\\
{u_y}\\
\end{bmatrix}.
$
